TITLE

### 2021-02-25 outputs/Paper.Rmd
update

The first six rows of raw data is shown in the table1 below. (Table \@ref(tab:rowdata))
```{r rowdata, echo=FALSE}
#plot row data set in table
  head(simulated_data)%>%
  select(-size)%>%
  kableExtra::kbl(caption = "First 6 rows Raw data ") %>%
  kableExtra::kable_styling(latex_options = "scale_down") # use scale_down option to make the font
```

>>>>

The first six rows of raw data is shown in the table1 below. (Table \@ref(tab:rowdata))
```{r rowdata, echo=FALSE}
#plot row data set in table
  head(simulated_data,10)%>%
  select(-size)%>%
  kableExtra::kbl(caption = "First 6 rows Raw data ") %>%
  kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
  kable_styling()
```
